Qualifying Report

### 2019-01-10 Source/QualifyingReport/QualifyingReport.tex
QR work done

% HEADER BEGINS
\documentclass[12pt, twoside, a4paper]{article}
%% Packages
\input{settings/packages}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{fancyhdr}
%% Page Settings
\input{settings/page}
%% Own Commands
\pagestyle{fancy}
\fancyhf{}
\fancyhead[CE,CO]{\leftmark}
\fancyfoot[CE,CO]{Early Detection of MCI that progresses to dementia - An Interdisciplinary Approach}
\fancyfoot[LE,RO]{\thepage}

\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{1pt}
\input{settings/macros}
\title{Qualifying Report}
\date{2019-01-07}
\author{Jomar Alcantara}
% HEADER ENDS
% DOCUMENT BEGINS
\begin{document}
\maketitle
\newpage
\begin{abstract}

\end{abstract}

@@

\section{Overview of Problem}

@@

\section{Literature Review}

@@

\includegraphics[width=240px, height=150px]{images\BCTPicture.png}

@@

\includegraphics[width=240px, height=150px]{\images\picnic-scene.jpg}

@@

\section{Initial Study of the Presidents corpus}
\subsection{Background}

\subsection{Methods}
I took 46 transcripts of Ronald Reagan’s (RR) press conferences from 1981 to 1988 and compared them with 134 press conferences by George H. W. Bush (GHWB) and 25 press conferences conducted by Donald J. Trump (DJT).  I analyzed transcripts for lexical features shown to change longitudinally with dementia  (for a comprehensive review of these, see the literature review above). For this collection of documents, I generated a number of features which looked at a number of different aspects of each document. These features encompassed, word level, sentence level and document level features and included a number of features contained in the study by Berisha and Liss with the aim of replicating and extending on their findings. These findings were. number of unique words, non-specific nouns and fillers and low imageability (LI) verbs. Imageability is characterized, according to Berisha and Liss, as the ease with which a term gives rise to a sensory .mental image. I compared the trends described in the transcripts of RR and GHWB, but also included DT. Berisha and Liss originally made the comparison as it GHWB (GHWB - age at the start of presidency - 64 years, 222 days) was the closest match to RR in terms of age (RR  - age at the start of presidency, 69 yeaars and 349 days). However, with the inauguration of Trump, he now is the closest comparible president in terms of age (DJT - age at the start of presidency - 70 years, 220 days). It would be interesting to look at a comparison of RR and DJT to see whether the comparisons made by Berisha and Liss hold true with this more appropriate match (in terms of age). DJT as with GHWB has no known diagnosis of AD. I used the press conference transcripts in the American Presidency Project (APP) archive as a data source for this project. The APP is a comprehensive and organized searchable database of presidential documents, including transcripts of speeches, transcripts of news conferences, and other public documents.
\subsubsection{Pre-processing}
To generate the files necessary for analysis, I downloaded each transcript and performed the following changes. I omitted the prepared statement by the president and any speech by other individuals. I started each transcript at the beginning of the first answer to a question. I filtered any annotations that were added to the transcript, including any references or clarifications, and any laughter. It's worth noting that there appears to be a difference in how 'hesitations' were marked down between each president, for RR hesitations were marked by a single hyphen whereas for GWB hesitations are marked by a double hyphen. In order to maintain consistency when parsing through the documents, I have changed both types of hesitation to be marked by a single hyphen. I also omitted one word sentences as this data would, from a theoretical perspective, not be relevant for language analysis. I did not control for the length of the document, but generated features which would normalise by the length of the document. I therefore was able to include all press conferences by both Ronald Reagan and George H.W. Bush where there was a question and answer session conducted at least in part by the sitting president (2 press conferences of GWB were ommited due to a lack of a question and answer session).
\subsection{Results}
\subsection{Discussion}
\subsection{Conclusion}

\section{Future Work}
\subsection{Introduction}

@@

\subsubsection{Task 6 - Thesis Writing}

\subsection{Risk Assessment}
In this section, I look at the potential difficulties that may produce a delay to the proposed research, define any strategies that have already been put in place to account for this as well as define any other potential solutions.
\subsubsection{Delay in data collection}

\subsubsection{Rejected Publications}

\subsubsection{Rejected NHS Ethics}

\subsection{Ethical Considerations}
In this section I discuss the ethical considerations related to this project and any adjustments that I have made to my research because of these considerations. I am aware of the code of human  research ethics published by the British Psychological Society \cite{Society2012} and my research has been designed in a way that fits with these guidelines.
\subsubsection{Risk}
I will be working with a middle-aged to elderly population who have identified in some way that there is a difficulty with cognition. However, I do not anticipate working with vulnerable groups, those lacking capacity or individuals in a dependant or unequal relationship. Should any participants I am working with lose capacity during the course of the study, I will remove that participants details and data from the study.
\par
\subsubsection{

@@

\section{Conclusion}

>>>>

% HEADER BEGINS
\documentclass{book}
%% Packages
\input{settings/packages}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{fancyhdr}
%% Page Settings
\input{settings/page}
%% Own Commands
\pagestyle{fancy}
\fancyhf{}
\fancyhead[CE,CO]{\leftmark}
\fancyfoot[CE,CO]{Early Detection of MCI that progresses to dementia - An Interdisciplinary Approach}
\fancyhead[LE,RO]{\thepage}

\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{1pt}
\input{settings/macros}
\title{Qualifying Report}
\date{2019-01-07}
\author{Jomar Alcantara}
% HEADER ENDS
% DOCUMENT BEGINS
\begin{document}
\maketitle

@@

\chapter{Overview of Problem}

@@

\chapter{Literature Review}

@@

\includegraphics[width=240px, height=150px]{images/BCTPicture.png}

@@

\includegraphics[width=240px, height=150px]{images/picnic-scene.jpg}

@@

\chapter{Initial Study of the Presidents corpus}
\subsection{Background}

\subsection{Methods}
I took 46 transcripts of Ronald Reagan’s (RR) press conferences from 1981 to 1988 and compared them with 134 press conferences by George H. W. Bush (GHWB) and 25 press conferences conducted by Donald J. Trump (DJT).  I analyzed transcripts for lexical features shown to change longitudinally with dementia  (for a comprehensive review of these, see the literature review above). For this collection of documents, I generated a number of features which looked at a number of different aspects of each document. These features encompassed, word level, sentence level and document level features and included a number of features contained in the study by Berisha and Liss with the aim of replicating and extending on their findings. These findings were. number of unique words, non-specific nouns and fillers and low imageability (LI) verbs. Imageability is characterized, according to Berisha and Liss, as the ease with which a term gives rise to a sensory .mental image. I compared the trends described in the transcripts of RR and GHWB, but also included DT. Berisha and Liss originally made the comparison as it GHWB (GHWB - age at the start of presidency - 64 years, 222 days) was the closest match to RR in terms of age (RR  - age at the start of presidency, 69 yeaars and 349 days). However, with the inauguration of Trump, he now is the closest comparible president in terms of age (DJT - age at the start of presidency - 70 years, 220 days). It would be interesting to look at a comparison of RR and DJT to see whether the comparisons made by Berisha and Liss hold true with this more appropriate match (in terms of age). DJT as with GHWB has no known diagnosis of AD. I used the press conference transcripts in the American Presidency Project (APP) archive as a data source for this project. The APP is a comprehensive and organized searchable database of presidential documents, including transcripts of speeches, transcripts of news conferences, and other public documents.
\subsubsection{Pre-processing}
To generate the files necessary for analysis, I downloaded each transcript and performed the following changes. I omitted the prepared statement by the president and any speech by other individuals. I started each transcript at the beginning of the first answer to a question. I filtered any annotations that were added to the transcript, including any references or clarifications, and any laughter. It's worth noting that there appears to be a difference in how 'hesitations' were marked down between each president, for RR hesitations were marked by a single hyphen whereas for GWB hesitations are marked by a double hyphen. In order to maintain consistency when parsing through the documents, I have changed both types of hesitation to be marked by a single hyphen. I also omitted one word sentences as this data would, from a theoretical perspective, not be relevant for language analysis. I did not control for the length of the document, but generated features which would normalise by the length of the document. I therefore was able to include all press conferences by both Ronald Reagan and George H.W. Bush where there was a question and answer session conducted at least in part by the sitting president (2 press conferences of GWB were ommited due to a lack of a question and answer session).
\subsubsection{Feature Selection}
\subsection{Results}
\subsection{Discussion}
\subsection{Conclusion}

\chapter{Future Work}
\subsection{Introduction}

@@

\subsubsection{Task 6 - Thesis Writing}
The writing of the thesis, including additional over-running data analysis is planned for the last six months of the project (Oct '20 to Mar '21).

\subsection{Risk Assessment}
In this section, I look at the potential difficulties that may produce a delay to the proposed research, define any strategies that have already been put in place to account for this as well as define any other potential solutions.
\subsubsection{Delay in data collection}
When working with a clinical population, the collection of data can be subject to delays. This can be for a number of reasons including but not limited to sickness (patient or researcher), unavailability of participant for another reason or unavailability of venue to collect data. The collection of data could also be subject to delays due to ethical approval for the research being delayed. For individual participants unavailability, flexibility has been built into the data collection schedule to allow for an extra month (capacity for one additional cohort) of data collection per collection cycle. 
\subsubsection{Rejected Publications}
For each task defined above, with the exception of task 2 and task 6 I have identified suitable conferences at which I can present my work. With the target conferences identified every effort will be made to meet the submission deadlines for these conferences. If submissions are rejected at these conferences, I will identify alternative conferences to present at. 
\subsubsection{Rejected NHS Ethics and/or University Ethics}
Every effort will be made to submit a complete ethics application through the NHS. However, in the event that there is a delay in the ethical approval process then data collection will proceed with a priority placed on the control group. Future cohorts will then have proportionally more clinical participants until the research meets it's target numbers.  
\subsection{Ethical Considerations}
In this section I discuss the ethical considerations related to this project and any adjustments that I have made to my research because of these considerations. I am aware of the code of human  research ethics published by the British Psychological Society \cite{Society2012} and my research has been designed in a way that fits with these guidelines.
\subsubsection{Risk}
I will be working with a middle-aged to elderly population who have identified in some way that there is a difficulty with cognition. However, I do not anticipate working with vulnerable groups, those lacking capacity or individuals in a dependant or unequal relationship. Should any participants I am working with lose capacity during the course of the study, I will remove that participants details and data from the study.
\par
\subsubsection{Informed Consent}

@@

\chapter{Conclusion}
